Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-11-04 neurips-20/infinite-outcomes.tex
Adding sufficient conditions from citing examples and adding a definition of \otimes

\documentclass[12pt]{article}
\linespread{1.05}
%\usepackage{fancyhdr}
%\usepackage{mathptmx}
%\usepackage{sidecap}
\usepackage{amsfonts, amsmath, amsthm, amssymb, graphicx, verbatim}
\usepackage[margin=1.0in]{geometry}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{amsfonts, amsmath, amsthm, amssymb, graphicx, verbatim} % For math fonts, symbols and environments
\usepackage{wrapfig} % Allows wrapping text around tables and figures
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{bbm}
\usepackage{thm-restate}
%\usepackage[backend=bibtex, style=footnote-dw]{biblatex}
%\addbibresource{diss.bib}

@@

\begin{definition}[Effective Domain]
	The \emph{effective domain} of a convex function $f: X \to \bar \reals$ is the set $S \subseteq X = \{x \in X : f(x) < \infty\}$,
\end{definition}

Let $(\Y, \B_\Y, p)$ define a measure space, where $\B_\Y$ is the $\sigma$-algebra of Borel sets on $\Y$.
If we are given a loss $f(u,y)$, we want to understand when $\partial \{\E_p f(\cdot,Y)\} = \E_p \partial f(\cdot,Y)$.

Note: expectation of a closed-valued multifunction $G:\Y \to 2^\reals$ is defined $\E_p G = \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\B_\Y), \nu(y) \in G(y) a.s.\})$.

\subsection{Definitions needed}
\begin{definition}[Measurable multifunction]
	A multifunction $F:\Y \to \reals^d$ is measurable iff for every open $E \subseteq \reals^d$, we have $F^{-1}(E) \in \B_\Y$. \jessie{Check?? Apparently in \cite{aubin2009set} but I can't find it easily.}
\end{definition}

\begin{definition}[$\A$-normal convex integrand]
	A function $f : \reals^d \times \Y \to \bar \reals$ is an $\A$-normal convex integrand if the map
	\begin{equation}
	y \mapsto \epi(f(\cdot, y))  = \{(u, \alpha) \in \reals^{d+1} : \alpha \geq f(u,y)\}
	\end{equation}
	is a closed-convex-valued measurable multifunction.
\end{definition}

\section{Result}
\begin{corollary}[\cite{rockafellar1982interchange,ioffe1969minimization}]
	Suppose $f$ is an $\B_\Y$-normal convex integrand such that $F(x) < \infty$ whenever $x \in \dom(f(\cdot,y))$ almost surely, where $F(x) = \E_p f(x,Y)$.

@@

\section{Examples}
We verify the satisfaction of the following three assumptions of the corollary:
\begin{enumerate}
	\item $f$ is a $\B_\Y$-normal convex integrand.
	\item $F(u) < \infty$ for $u \in \effdom(f(\cdot,y))$ almost surely (on $y$).
	\item There exists $x_0 \in \reals^d$ so that $\E_p f(x_0, Y)$ is (a) finite (b) continuous at $x_0$ and (c) $y \mapsto \cl \dom (f(\cdot, y))$ is almost surely constant.
\end{enumerate}
\subsection{$f(u,y) = |u|$.}

@@

First, $G : y \mapsto \{(u,\alpha) : \alpha \geq |u| \}$ can be verified that the function is closed, convex-valued, and measurable.
Second, since $\E_p f(u,Y) = |u|$, $u \in \effdom(f)$ (almost surely) implies $u \in \reals$, and by substitution, we have $\E_p f(u,Y) = |u| < \infty$.
Third, Take $x_0 = 0$.  For all $p$, we have $\E_p f(x_0, Y) = 0$, and $f$ is continuous at $0$.

@@

Restrict to convex losses that are $\A$-normal convex integrands... is this the same as identifiable functions?
\jessie{Reminds me of~\cite[Theorem 5]{steinwart2014elicitation}, but they require $\Gamma$ to be real valued and strictly locally non-constant...}
\jessie{Also related~\cite[Theorem 2]{gneiting2011making}}

@@

\begin{conjecture}
	If a convex loss $L:\reals^d \times \Y \to \reals$ elicits a nonempty property $\Gamma$, then there is a function $V:\reals^d \times\Y \to \reals$ such that $L(r,y) = \int V(r,y) dy$.
\end{conjecture}

\begin{theorem}[Theorem 2]
	Let a property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
	Then if a convex loss \jessie{$\A$-normal convex integrand? such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$} $L : \reals^d \times \Y \to \reals$ indirectly elicits $\gamma$, there is a flat $F$ with $p \in F \cap \P \subseteq \gamma_r$ with $\codim(F) \leq d$.
\end{theorem}
\begin{proof}
	Consider the probability space $(\Y, \A, p)$ \jessie{Don't think $\B_\Y$ is necessary... generic $\A$ is fine?}, where $p \in \P$, and let $\Gamma := \prop{L}$.
	Moreover, suppose $(L, \psi)$ indirectly elicits $\gamma$.
	By definition of properties, there is some $u \in \Gamma(p)$.

@@

	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \E_p L(u,Y)$.
	Since, for each $p \in \P$ by Lemma~\ref{lem:conditions-sat}, $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we also have $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\B_\Y), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$.
	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists in the closure of this set.
	We now take $F := \ker(\nu) \cap \P$.

@@

\begin{lemma}\label{lem:conditions-sat}
	For convex $L : \reals^d \times \Y \to \reals$ eliciting the nonempty property $\Gamma:\P\toto\R$, if $\P$ is a set such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d$ and $p \in \P$, then the conditions of \cite[Corollary 1]{rockafellar1982interchange} are satisfied.
\end{lemma}
\begin{proof}
	First, we enumerate the conditions of \cite[Corollary 1]{rockafellar1982interchange}.\begin{enumerate}
		\item $L$ is a $\B_\Y$-normal convex integrand.
		\item $\E_p L(u,Y) < \infty$ for $u \in \effdom(L(\cdot,y))$ almost surely (on $y$).
		\item There exists $x_0 \in \reals^d$ so that $\E_p f(x_0, Y)$ is (a) finite (b) continuous at $x_0$ and (c) $y \mapsto \cl \dom (f(\cdot, y))$ is almost surely constant.
	\end{enumerate}

As we constrain $L$ to be real-valued, the effective domain and domain are equal, and assumed to be $\reals^d$.
The first condition follows as a corollary of \jessie{another result? do we need to prove this?  see conjecture above}
Therefore, the second condition is satisfied when $\E_p L(u,Y)$ is finite for all $u \in \reals^d$, by assumption on $\P$.
Third, for each $p$, take $x_0 \in \Gamma(p)$.
As $L$ is finite, we know that $\E_p L(\Gamma(p), Y)$ is finite, and part (c) follows by assumption on $L$.
Moreover, $\E_p L(\cdot, Y)$ is continuous at $x_0$ by convexity of $L$ in its first argument and the assumption that $L(u,y)$ is finite for all $u,y$.
\end{proof}

>>>>

\documentclass[12pt]{article}
\linespread{1.05}
%\usepackage{fancyhdr}
%\usepackage{mathptmx}
%\usepackage{sidecap}
\usepackage{amsfonts, amsmath, amsthm, amssymb, graphicx, verbatim}
\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{booktabs} % Top and bottom rules for table
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{amsfonts, amsmath, amsthm, amssymb, graphicx, verbatim} % For math fonts, symbols and environments
\usepackage{wrapfig} % Allows wrapping text around tables and figures
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{bbm}
\usepackage{thm-restate}
%\usepackage[backend=bibtex, style=footnote-dw]{biblatex}
%\addbibresource{diss.bib}

@@

\begin{definition}[Effective Domain]
	The \emph{effective domain} of a {\color{blue} convex} function $f: X \to \bar \reals$ is the set $S \subseteq X = \{x \in X : f(x) < \infty\}$,
\end{definition}

Let $(\Y, \A, p)$ define a ($\sigma$-finite) measure space.
If we are given a loss $f(u,y)$, we want to understand when $\partial \E_p f(\cdot,Y) = \E_p \partial f(\cdot,Y)$.

\begin{definition}[Expectation of a closed-valued multifunction]
	 $G:\Y \to 2^\reals$ is defined.
	 $\E_p G = \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in G(y)\,\, a.s.\})$.
\end{definition}

\begin{definition}[$\otimes$, \cite{folland1999real} Page 20]
	Consider the space $X = \reals^d \times \Y$ and $\pi_\alpha:X \to X_\alpha$ the coordinate maps, where $\alpha \in \{1,2\}$.
	If $\A_\alpha$ is a $\sigma$-algebra on $X_\alpha$ for each $\alpha$,the \emph{product $\sigma$-algebra} on $X$ is the $\sigma$-algebra generated by 
		\begin{equation*}
		\{ E_1 \times E_2 : E_\alpha \in \A_\alpha \}~.~
		\end{equation*}
		We denote this $\sigma$-algebra by $\A_1 \otimes \A_2$.
\end{definition}

\subsection{Definitions needed}
\begin{definition}[Measurable multifunction~\cite{aubin2009set} Definition 8.1.1]
	Consider a measurable space $(\Y, \A)$ and set-valued function $H: \Y \to 2^{\reals^{d+1}}$ with closed images.

	The multifunction $H:\Y \to 2^{\reals^{d+1}}$ is $\A$-measurable iff for every open $E \subseteq \reals^{d+1}$, we have $H^{-1}(E) = \{y \in \Y: H(y) \cap E \neq \emptyset \} \in \A$.
\end{definition}

\begin{definition}[$\A$-normal convex integrand]
	A function $f : \reals^d \times \Y \to \bar \reals$ is an $\A$-normal convex integrand if the map
	\begin{equation}
	H^f : y \mapsto \epi(f(\cdot, y))  = \{(u, \alpha) \in \reals^{d+1} : \alpha \geq f(u,y)\}
	\end{equation}
	is a closed convex-valued measurable multifunction.
\end{definition}
Note: the above map is closed if and only if $H^f$ is lower semi-continuous (in $y$), and is convex-valued as $f(\cdot,y)$ is convex in $\reals^d$ for all $y \in \Y$.

%\jessie{Think on how to show this for any expected loss; show true if ??? (e.g. $f$ continuous in $y$)}
\jessie{See who has used this result?}

\begin{definition}[$\A$ convex normal integrand via \cite{castaing2006convex} Definition VII.1]
	A mapping $f : \reals^d \times\Y \to \reals$ is called \emph{normal integrand} if for every fixed $y \in \Y$, we have $f(\cdot, y)$ is lower semi-continuous and $f$ is $\B(\reals^d) \otimes \A$-measurable.
	$f$ is called a \emph{convex normal integrand} if it is a normal integrand and for every fixed $y \in \Y$, we have $f(\cdot,y)$ convex.
\end{definition}

Now we just need our loss to be lower semi-continuous and measurable, and the definitions are shown to be equivalent by~\cite[Lemma VII-1 (page 196)]{castaing2006convex}.

\subsection{Sufficient conditions for normal integrands}
The first comes from~\cite[Lemma 2]{kucia1995normal} but doesn't help me at all lol.
\begin{condition}
	If $f$ is a Caratheodory\jessie{not sure what this is tbh} integrand and $D$ has a Castaing representation, then $f$ is a normal integrand.
	Note $D \subset \Y \times X$, where $X$ is a topological space.
\end{condition}

\begin{condition}[\cite[Lemma 4.5]{dupacova1988asymptotic}]
	$f$ is LSC and Lipschitz.
\end{condition}

\begin{condition}[Appendix A Dekel12]
	$f(\cdot, y)$ is $L$-smooth for any $y$. % and $f(\cdot, y)$ is differentiable.
\end{condition}

\section{Result}
\begin{corollary}[\cite{rockafellar1982interchange,ioffe1969minimization}]
	Suppose $f$ is an $\A$-normal convex integrand such that $F(x) < \infty$ whenever $x \in \dom(f(\cdot,y))$ almost surely, where $F(x) = \E_p f(x,Y)$.

@@

\section{Examples}
We verify the satisfaction of the following three assumptions of the corollary:
\begin{enumerate}
	\item $f$ is a $\A$-normal convex integrand.
	\item $F(u) < \infty$ for $u \in \effdom(f(\cdot,y))$ almost surely (on $y$).
	\item There exists $x_0 \in \reals^d$ so that $\E_p f(x_0, Y)$ is (a) finite (b) continuous at $x_0$ and (c) $y \mapsto \cl \dom (f(\cdot, y))$ is almost surely constant.
\end{enumerate}
\subsection{$f(u,y) = |u|$.}

@@

First, $H : y \mapsto \{(u,\alpha) : \alpha \geq |u| \}$ can be verified that the function is closed, convex-valued, and measurable.
Second, since $\E_p f(u,Y) = |u|$, $u \in \effdom(f)$ (almost surely) implies $u \in \reals$, and by substitution, we have $\E_p f(u,Y) = |u| < \infty$.
Third, Take $x_0 = 0$.  For all $p$, we have $\E_p f(x_0, Y) = 0$, and $f$ is continuous at $0$.

@@

Restrict to losses that are $\A$-normal convex integrands.
%... is this the same as identifiable functions?
%\jessie{Reminds me of~\cite[Theorem 5]{steinwart2014elicitation} and \cite[Theorem 2]{gneiting2011making}, but the former requires $\Gamma$ to be real valued and strictly locally non-constant...}

@@

\begin{theorem}[Theorem 2]
	Let a property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
	Let $L : \reals^d \times \Y \to \reals$ be a convex loss\footnote{must be a $\A$ convex normal integrand} such that such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$.
	If $L$ indirectly elicits $\gamma$, there is a flat $F$ with $p \in F \cap \P \subseteq \gamma_r$ with $\codim(F) \leq d$.
\end{theorem}
\begin{proof}
	Consider the probability space $(\Y, \A, p)$, where $p \in \P$, and let $\Gamma := \prop{L}$.
	Moreover, suppose $(L, \psi)$ indirectly elicits $\gamma$.
	By definition of properties, there is some $u \in \Gamma(p)$.

@@

	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \E_p L(u,Y)$.
	Since, for each $p \in \P$ by Lemma~\ref{lem:conditions-sat}, $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we also have $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y) := \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$.
	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists in the closure of this set.
	We now take $F := \ker(\nu) \cap \P$.

@@

\begin{lemma}\label{lem:conditions-sat}
	For convex $L : \reals^d \times \Y \to \reals$ eliciting the nonempty property $\Gamma:\P\toto\R$, if $\P$ is a set such that $\E_p L(u,Y) < \infty$ for all $u \in \reals^d$ and $p \in \P$, then the conditions of \cite[Corollary 1]{rockafellar1982interchange} are satisfied.
\end{lemma}
\begin{proof}
	First, we enumerate the conditions of \cite[Corollary 1]{rockafellar1982interchange}.\begin{enumerate}
		\item $L$ is a $\A$-normal convex integrand.
		\item $\E_p L(u,Y) < \infty$ for $u \in \effdom(L(\cdot,y))$ almost surely (on $y$).
		\item There exists $x_0 \in \reals^d$ so that $\E_p f(x_0, Y)$ is (a) finite and (b) continuous at $x_0$
		\item $y \mapsto \cl \dom (f(\cdot, y))$ is almost surely constant.
	\end{enumerate}

As we constrain $L$ to be real-valued, the effective domain and domain are equal, and assumed to be $\reals^d$.
The first condition follows by assumption that $L$ is $\B(\reals^d) \otimes \A$-measurable and lower semi-continuous.
Therefore, the second condition is satisfied when $\E_p L(u,Y)$ is finite for all $u \in \reals^d$, by assumption on $\P$.
Third, for each $p$, take $x_0 \in \Gamma(p)$.
As $L$ is finite, we know that $\E_p L(\Gamma(p), Y)$ is finite.
Moreover, $\E_p L(\cdot, Y)$ is continuous at $x_0$ by convexity of $L$ in its first argument and the assumption that $L(u,y)$ is finite for all $u,y$. \jessie{Don't think this is accurate}
The final condition follows by assumption on $L$.
\end{proof}
